TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-20 paper/paper.tex
Update related work; give overview of sections in introduction

TODO in the next section blah, then blah, and finally blah.

@@

% Copied from proposal

% todo make this logical
In 2010, the algorithm DCTCP was described in an
article\cite{dctcp-congestion-original} and published as RFC8257 in
2017\cite{dctcp-congestion}. DCTCP is optimized for datacenters and provides a
high-burst tolerance, low latency, and high throughput when the datacenter has
a small part of the buffer available\cite{dctcp-congestion}. In 2016 another
algorithm was proposed: BBR. This is a TCP congestion algorithm created by
Google, which achieves higher bandwidths and lower latencies compared to other
TCP congestion methods\cite{bbr-congestion}. A comparison of BBR with
CUBIC\cite{bbr-congestion-comparison} shows that the BBR node pushes the CUBIC
node away in bandwidth when using small buffers. The BBR node gets more
bandwidth allocated than the CUBIC node.

The TCP congestion control algorithm BBR is discussed in \cite{bbr-congestion}.
The journal contains a performance test of the BBR algorithm and a comparison
between the BBR algorithm and the CUBIC algorithm, where a noticeable
difference in bandwidth allocation is shown when using small buffers.

In \cite{multiple-congestion} a performance analysis of multiple TCP congestion
control algorithms is performed. This research does not include the new
congestion control algorithms we want to analyze and does not include the
datacenter context.

In \cite{dctcp-congestion-original} an algorithm is proposed to avoid
congestion within datacenters. The authors describe an algorithm that maintains
a small buffer occupancy and has an early detection of congestion.

\section{Method}

@@

\section{Results}

@@

\subsection{TCP Congestion Algorithms}

@@

\subsection{Theoretical Algorithm Characteristics}

@@

\subsection{Experiments' Results}

@@

\section{Discussion}

\section{Conclusion}

>>>>

In the next section, we will discuss related work. Section \ref{sec:method}
describes our methods: how we selected algorithms to test, how we tested their
performance, and how we chose network conditions to simulate. Section
\ref{sec:results} describes the results of our research: the algorithms we
chose to test are described in \ref{sub:chosen-algos}, a theoretical analysis
of those is described in \ref{sub:algos-theoretical}, and experimental results
can be found in \ref{sub:experiment-results}. We discuss our results in section
\ref{sec:discussion} and draw conclusions in section \ref{sec:conclusion}.

@@

In 2010, the algorithm DCTCP was described by Mohammad Alizadeh et
al.\cite{dctcp-congestion-original} and published as
RFC8257\cite{dctcp-congestion} in 2017. DCTCP is optimized for datacenters and
provides a high-burst tolerance, low latency, and high throughput when the
datacenter has a small part of the buffer available\cite{dctcp-congestion}.

In 2016 another algorithm was proposed: BBR. This is a TCP congestion algorithm
created by Google, which achieves higher bandwidths and lower latencies
compared to other TCP congestion methods\cite{bbr-congestion}. A comparison of
BBR with CUBIC\cite{bbr-congestion-comparison} shows that the BBR node pushes
the CUBIC node away in bandwidth when using small buffers. The BBR node gets
more bandwidth allocated than the CUBIC node.

The TCP congestion control algorithm BBR is discussed by Neal Cardwell et
al.\cite{bbr-congestion} The article contains a performance test of the BBR
algorithm and a comparison between the BBR algorithm and the CUBIC algorithm,
where a noticeable difference in bandwidth allocation is shown when using small
buffers.

A. Esterhuizen and A.E. Krzesinski\cite{multiple-congestion} analyse the
performance of multiple TCP congestion control algorithms, specifically: Reno,
BIC, CUBIC, HighSpeed TCP, TCP-Hybla, TCP-Illinois, TCP Low Priority,
TCP-Vegas, TCP-Westwood, TCP-YeAH, and Scalable TCP.

\section{Method}\label{sec:method}

@@

\section{Results}\label{sec:results}

@@

\subsection{TCP Congestion Algorithms}\label{sub:chosen-algos}

@@

\subsection{Theoretical Algorithm Characteristics}\label{sub:algos-theoretical}

@@

\subsection{Experiments' Results}\label{sub:experiment-results}

@@

\section{Discussion}\label{sec:discussion}

\section{Conclusion}\label{sec:conclusion}
